Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-03 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
exaplmple arreglado
implmented arreglado

\item {\bf Graph-Neo4J} 
 Collaborative IEC (C-IEC) systems need to store highly connected data, as it is common 
 in current applications like social networks. In order to deal with large datasets of connected 
 data found in these systems, graph databases \cite{angles2012comparison} have been proposed 
 as an alternative to relational databases which have performance limitations when dealing with 
 highly connected data \cite{holzschuher2013performance}.
 A graph is proposed for modeling the social network of users, their interaction with 
 candidate solutions, and the relationships between them in the population.
 The graph database system used in the implementation is Neo4J as it is
 a scalable solution \cite{miller2013graph,holzschuher2013performance}, and well 
 supported and documented in PaaS infrastructures like Heroku. The Cypher query 
 language it used to retrieve views from the graph.
 An exaplmple query is shown in figure \ref{fig:cypher} where the relations 
 between users and solutions are presented.

@@

\item {\bf Evolution}    
The evolutionary algorithm is decoupled from the data model, the algorithm 
could be implemented as an EvoWorker \cite{garcia2013evospace}, use an external library, 
or even assigned to humans. An additional tool was implmented for a human based evolution, 
where volunteers select the parents of the next generation and upload the 
new individuals \cite{de2014artists}.  
\end{itemize}

>>>>

\item {\bf Graph-Neo4J} 
 Collaborative IEC (C-IEC) systems need to store highly connected data, as it is common 
 in current applications like social networks. In order to deal with large datasets of connected 
 data found in these systems, graph databases \cite{angles2012comparison} have been proposed 
 as an alternative to relational databases which have performance limitations when dealing with 
 highly connected data \cite{holzschuher2013performance}.
 A graph is proposed for modeling the social network of users, their interaction with 
 candidate solutions, and the relationships between them in the population.
 The graph database system used in the implementation is Neo4J as it is
 a scalable solution \cite{miller2013graph,holzschuher2013performance}, and well 
 supported and documented in PaaS infrastructures like Heroku. The Cypher query 
 language it used to retrieve views from the graph.
 An example query is shown in figure \ref{fig:cypher} where the relations 
 between users and solutions are presented.

@@

\item {\bf Evolution}    
The evolutionary algorithm is decoupled from the data model, the algorithm 
could be implemented as an EvoWorker \cite{garcia2013evospace}, use an external library, 
or even assigned to humans. An additional tool was implemented for a human based evolution, 
where volunteers select the parents of the next generation and upload the 
new individuals \cite{de2014artists}.  
\end{itemize}
